Criteria for evaluating reproducibility

### 2017-04-04 reproducibility_criteria.Rmd
Edits to reproducibility criteria for spelling; update example_tibble.R
Update example_tibble.R with new reproducibility criteria scoring

0. All steps were performed manually with no choesive document describing exactly what was done
1. Steps were performed manually, but with a detailed record (e.g. pasted commands in a text file)
2. A set of runnable scripts were used, but have to be executed individually or the outputs require manually modifications
3. A makefile or master script was provided that runs the entire analysis from raw data to published results

>>>>

0. All steps were performed manually with no cohesive document describing exactly what was done
1. Steps were performed manually, but with a detailed record (e.g. pasted commands in a text file)
2. A set of runnable scripts were used, but have to be executed individually or the outputs require manual modifications
3. A makefile or master script was provided that runs the entire analysis from raw data to published results
